Structuring Theories with Implicit Morphisms

### 2018-10-14 example.tex
added links for bands

There are various morphisms between them that describe the lattice structure of the corresponding varieties of bands.
All of these map the constants from \cn{Band} to themselves and the axiom $a$ to a proof.\ednote{@DM: no need to give the morphisms, but link to the online resource if you have time to work them all out}
We make all of these morphisms implicit.
It is straightforward to prove that the diagram commutes: any two morphisms are identical except for assignment for the axiom.
Here, \mmt can discharge the proof obligation easily using proof irrelevance.

>>>>

There are various morphisms between them that describe the lattice structure of the corresponding varieties of bands.
All of these map the constants from \cn{Band} to themselves and the axiom $a$ to a proof.\footnote{Our formalization of the lattice of bands using implict morphisms can be found at \url{https://gl.mathhub.info/MitM/smglom/blob/devel/source/algebra/bands.mmt} and \url{https://gl.mathhub.info/MitM/smglom/blob/devel/source/algebra/lattice.mmt}}
We make all of these morphisms implicit.
It is straightforward to prove that the diagram commutes: any two morphisms are identical except for assignment for the axiom.
Here, \mmt can discharge the proof obligation easily using proof irrelevance.
